Clustering exploration for `r params$sample_id`

### 2024-09-05 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

The aim is to explore the clustering and label transfers for the sample `param$sample_id` =

```{r}
params$sample_id
```

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

>>>>

The aim is to explore the clustering and label transfers for the sample `r param$sample_id`.

@@
